### 2017-06-28 paper.tex
Add files via upload

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{amssymb,amsmath,array}

\usepackage{url}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Joint Neighborhood Subgraphs Link Prediction}

% a short form should be given in case it is too long for the running head
%\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Dinh Tran-Van$^1$ \and Alessandro Sperduti$^1$ \and Fabrizio Costa$^2$}
%
\authorrunning{Dinh Tran Van, Alessandro Sperduti, and Fabrizio Costa$^2$}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{$^1$ Department of Mathematics, Padova University, Italy\\
%via Trieste, 63, 35121 Padova, Italy\\
$^2$ Department of Computer Science, University of Exeter, United Kingdom\\ 
$\lbrace$dinh, sperduti$\rbrace$@math.unipd.it, f.costa@exeter.ac.uk
%\mailsc\\
}
%\url{http://www.springer.com/lncs}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
Graphs are common data structure used to represent data in which the relation between entities are encoded. A number of graph-based methods and systems have been proposed, varying from biology to recomendation to social network. Most methods have to take partially observed graphs as the input to proceed due to the lack of information. This prevents them from showing promissing results. Link prediction becomes an effective paradigm to solve this problem. However, most existing link prediction methods are based on the transitive manner which cannot effectively exploit graph structures. Here we propose a method that first represents each link between two nodes by a graph composed of their neighborhood subgraphs. We then employ a decompositional graph kernel to measure the similarity between links. An empirical experiment on diferent datasets proves that our proposed method shows the state of the art for link prediction.
\keywords{Link prediction, joint neighborhood subgraphs}
\end{abstract}

\section{Introduction}
A huge amount and variety of relational data are available in a wide range of fields. On the one hand, it provides an opportunity to build systems which automatically extract useful information. On the other hand, it raises challenges for machine learning and data scientists to design high performance predictive systems. A common data struture for representing relational data is graph whose nodes describe for entities and links depict their relations. We can easily see graph-based systems in different domains like biology, chemistry or networking. These systems require the data form used for their input as graphs. However, despite the availability of huge data, most graphs are only partially observed graphs. That means a number of actual links in each graph are absent or missing. Tackling this issue is a necessary condition to obtain high performance graph-based predictive systems. As a consequence, many link prediction methods have been proposed with the aim of recovering the missing links. A graph could be associtated with external information sources, so called "side information". Therefore, a link prediction method attempts to exploit the graph topology and side information to build a the model for predicting the presence or absence of link any between couple of nodes. An expected method is required to make use of both such kind of data sources. In this paper, we only focus on the topological information. Thus we the term link prediction methods to refer to topology-based link prediction methods.

Conerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning. Unsupervised learning methods compute the scores for node couples based on topological features and directly use these scores to consider non-observed links to be present or absent. Typical examples link prediction methods which fall into this class are Adamic-Adar \cite{adamic}, Katz \cite{katz}, Leicht-Home-Newman \cite{lhni}, etc. Supervised learning link prediction methods are based on a learning process which try to separate present links and absent links by their characteristics. A link prediction method via matrix factorization \cite{matrix-factorization} is for instance. This group of methods can also be further grouped into four subsets: feature-based models, graph regularization models, latent class models and latent feature models as presented in \cite{matrix-factorization}. For the performance, supervised methods tend to show better performance comparing to unsupervised ones in general. However, they normally face with the high compexity in term of computation and memory consumption.

The common feature of most existing supervised and unsupervised methods for link prediction is that they use transitive manner to exploit the graph structure. This manner normally does not show high discriminative capacity. Therefore, in this paper, we propose a novel supervised method named joint neighborhood subgraphs link prediction (JNSL). Our method first introduces a method to represent each link between two nodes as a graph composed by taking a union of neighborhood subgraphs rooted at these these corresponding nodes. It then adopts a decompositional graph kernel which allow to fully exploit graphs' structure to measure the similarity, one of the key point in machine learning algorithms.

\section{Method}
In this section, we describe our proposed link prediction method which is based on the graph structure exploitation only.
\subsection{Definitions and notation}
We consider a graph $G=(V,E)$ where $V$ is the set of nodes and $E$ is the set of links. The set $E$ can be devided into a subset of observed links (O) and a subset of unobserved links (U). The problem is that the set O is not a complete set. Therefore, \textit{link prediction} is the task that aims at exploiting graph structure to rank links in $U$ from the most to the least probable to be considered as observed links in $O$.

The \textit{distance} between two nodes $u$ and $v$, notated as $\mathcal{D}(u,v)$, is the length of the shortest path between them. The \textit{neighborhood} with radius $r$ of a node $v$ is the set of nodes
at a distance no greater than $r$ from $v$ and denoted by $N_r(v)$. The \textit{neighborhood subgraph} with radius $r$ of node $v$, denoted by $\mathcal{N}_{r}^{v}$,  is the subgraph formed by the nodes in the
neighborhood with radius $r$ of $v$ and the relative edges with endpoints in $N_r(v)$. The degree of a node $u$ denoted as $d(u)$ is the number of its neighborhood $d(u) = \mathcal{N}_{1}^{u}$.
\subsection{The neighborhood subgraph pairwise distance kernel}
The NSPDK \cite{nspdk} is an instance of convolution kernel \cite{convolution-kernel} where given a graph $G \in \mathcal{G}$ and two rooted graphs $A_u, B_v$, the relation $R_{r,d}(A_u, B_v, G)$ is true {\em iff} $A_u \cong \mathcal{N}_r^u$ is (up to isomorphism $\cong$) a neighborhood subgraph of radius $r$ of $G$ and so is $B_v \cong  \mathcal{N}_r^v$, with roots at distance $\mathcal{D}(u,v)= d$. We denote $R^{-1}$ as the inverse relation that returns all pairs of neighborhoods of radius $r$ at distance $d$ in $G$, $R^{-1}_{r,d}(G) = \lbrace A_u, B_v | R_{r,d}(A_u,B_v,G)=true\rbrace$. The kernel $\kappa_{r,d}$ over $\mathcal{G} \times \mathcal{G}$, counts the number of such fragments in common in two input graphs: 
\begin{center}
$\kappa_{r,d}(G,G^{'}) = 
\!\!\!\!\!\!\!\!\!\!\!\! 
\sum\limits_{\substack{A_u, B_v \ \in \ R_{r,d}^{-1}(G) \\ 
{A'}_{u'}, {B'}_{v'} \ \in \ R_{r,d}^{-1}(G')
}} \!\!\!\!\!\!\!\!\!\!\!\!  { { \textbf{1}_{A_{u} \cong A'_{u'}}} \cdot {
\textbf{1}_{B_{v} \cong B'_{v'}}} }$, 
\end{center}
\noindent where $\textbf{1}_{A \cong B}$ is the \textit{exact matching function} that returns 1 if $A$ is
isomorphic to $B$ and 0 otherwise.  Finally, the NSPDK is defined as $K(G,G') = \sum\limits_{r}{\sum\limits_{d}{\kappa_{r,d}(G,G')}}$, where for efficiency reasons, the values of $r$ and $d$ are upper bounded to a given maximal $r^*$ and $d^*$, respectively.

\subsection{Node labeling}
NSPDK takes labeled graphs as its input to proceed. Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure. Here, we propose to use node labeling fuctions $L$ that take into account node degrees for their labels such that $\ell(u) = \ell(v)$ if $|d(u) - d(v)|\leq \lambda$, in which $\lambda$ is a hyper parameter. It is due to the assumption that nodes with similar degrees tend to share common properties. The values of $\lambda$ depend on the histogram of graph node degree. We can use tuning in order to obtain suitable value for $\lambda$.
\subsection{Link representation}
In this section, we propose a method to represent links in the form of neighborhood subgraphs.

Let us consider two nodes $u$ and $v$ ($u, v \in V$), we first extract two neighborhood subgraphs with radius $R$ rooted at $u$ and $v$ to obtain $N_R(u)$ and $N_R(v)$, respectively. We then represent a link connecting $u$ and $v$ by a graph $G_{uv}$ formed by taking a union of these two achieved subgraphs: $G_{uv}= N_R(u) \cup N_R(v)$.
\subsection{Joint neighborhood subgraphs link prediction}
Given a graph $G(V,E)$ and a set of links $L = \lbrace(u,v)\ |\ (u,v)\in\ O\ or\ (u,v)\in U \rbrace$, our method consists five steps:
\begin{itemize}
	\item Node labeling: Nodes in $G$ are labeled using a defined node label function $\ell$.
	\item Link representing: Link in $L$ are represented as joint neighborhood subgraphs. As a result, we have a set of graphs $SG = \lbrace G_{uv}\ |\ (u,v) \in L \rbrace$
	\item Kernel computation: Obtained graph set $SG$ is used to compute a gram matrix, $K$, by using NSPDK. $K$ shows the similarities between graphs (links).
	\item Model configuration: $K$ is then fed into a kernel machine to build a model which tries to learn a function to separate observed links from non-observed ones in the sense of properties.
	\item Scoring and ranking: Now the model is used to return scores for coming links. These scores are used to rank links from the most to the least probable of being present in the graph.
\end{itemize}

\section{Experiment}
In this section, we intend to measure the performance of our proposed method and compare it with other link prediction methods. We follow the procedure used in \cite{matrix-factorization} which employs six datasets in different fields. Following, we give each dataset a short description.
\begin{itemize}
\item \textit{Protein }\cite{protein-protein}: the medium confidence network which encodes the interaction between proteins. It contains 2617 nodes and 11855 links.

\item \textit{Metabolic} \cite{metabolic}: a biological network which relates enzyme proteins and chemical compounds and includes 668 nodes and 2782 links.

\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference containing 2865 nodes and 4733 links.

\item \textit{Condmat} \cite{condmat}: a network of co-authors for condensed matter physists. This network has 14230 nodes and 1196 links.

\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: a network describing the dispute between countries. It consists of 130 nodes and 180 links.

\item \textit{Powergrid} cite{powergrid}: a network of electric powergrid in US. It has 4941 nodes and 6594 links.
\end{itemize}

We evaluate the performance of employed methods via a 10 splits. Each round, a given ratio of links will be used to train models, and the rest of links are used to test. For \textit{Protein}, \textit{Metabolic}, \textit{Nips} and \textit{Conflict} networks, we set the training ratio to 10$\%$ while the training ratio for \textit{Condmat} and \textit{Powergrid} to 90$\%$. The performance of each method is computed by taking an average of ROC-AUC over 10 rounds.

\textbf{Model Selection}: The values of different hyper-parameters are set by using a 3-fold on training set in which we use one fold for training and the rest two folds for validation. We tune the values of radius for extracting subgraphs $R$ in $\lbrace 1, 2 \rbrace$, $\lambda$ for node degree function in $\lbrace 1, 2 \rbrace$, for $r$ and $d$ parameters of NSPDK in $\lbrace  1, 2 \rbrace$ and $\lbrace  1, 2, 3 \rbrace$, respectively. Finally, the regularization tradeoff $C$ for the SVM is picked up in $\lbrace 10^{-4}, 10^{-3}, 10^{-2},\ 10^{-1}, 1,\ 10,\ 10^2, 10^3,\ 10^4 \rbrace$.

\section{Results and Discussion}
Table \ref{result_table} shows the performance of link prediction methods in ROC-AUC on six datasets. From the results on the table, we can group methods into two groups based on their performances: supervised methods and unsupervised methods. The performance of supervised methods are considerably higher than unsuperivsed ones in most cases, except in the Conflict dataset where Sup-Top outperforms Fact+Scores, but with a very small difference. Concerning supervised methods, JNSL outperforms Fact-Scores in all cases. The difference between their performance is small in PowerGrid and Protein datasets with 0.5$\%$ and 0.8$\%$, respectively.

\begin{table}
\caption{The performance in percentage on six datasets of different link prediction methods in which AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top: Liear regression running on unsupervised scores \cite{matrix-factorization}:, SVD \cite{matrix-factorization}:: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores. }
\centering
\setlength{\tabcolsep}{1mm}
\begin{tabular}{|c|c|c|c|c|c|c|}

\hline
         & \multicolumn{6}{c|}{\textbf{Datasets}}\\
 \hline
\textbf{Methods} & Protein & Metabolic & Nips & Condmat & Conflict & PowerGrid\\
\hline
AA & 56.4$\pm$0.5 & 52.4$\pm$0.5 & 51.2$\pm$0.2 & 56.7$\pm$1.4 & 50.7$\pm$0.8 & 58.9$\pm$0.3\\
PA & 75.0$\pm$0.3 & 52.4$\pm$0.5 & 54.3$\pm$0.5 & 71.6$\pm$2.6 & 54.6$\pm$2.4 & 44.2$\pm$01.0\\
SHP & 72.6$\pm$0.5 & 62.6$\pm$0.4 & 51.7$\pm$0.3 & 67.3$\pm$1.8 & 51.2$\pm$1.4 & 65.9$\pm$1.5\\
Katz & 72.7$\pm$0.5 & 60.8$\pm$0.7 & 51.7$\pm$0.3 & 67.3$\pm$1.7 & 51.2$\pm$1.4 & 65.5$\pm$1.6 \\
Sup-Top & 75.4$\pm$0.3 & 62.8$\pm$0.1 & 54.2$\pm$0.7 & 72.0$\pm$2.0 & 69.5$\pm$7.6 & 70.8$\pm$6.2\\
SVD & 63.5$\pm$0.3 & 53.8$\pm$1.7 & 51.2$\pm$3.1 & 62.9$\pm$5.1 & 54.1$\pm$9.4 & 69.1$\pm$2.6\\
Fact+Scores & 79.3$\pm$0.5 & 69.6$\pm$0.2 & 61.3$\pm$1.9 & 81.2$\pm$2.0 & 68.9$\pm$4.2 & 75.1$\pm$2.0 \\
JNSL & 80.1$\pm$0.8 & 72.5$\pm$0.7 & 62.1$\pm$0.8 & 88.6$\pm$2.3 & 72.0$\pm$0.9 & 75.6$\pm$0.7 \\
 \hline 
\end{tabular}
\label{result_table}
\end{table}
\section{Conclusion and Future Work}
In this paper, we have proposed an effective method for link prediction. Our method takes advantages from the way to represent links as joint neighborhood subgraphs and the employment of an convolution kernel that is able to efficiently exploit the graph structure. The results from the experiment show that our method is the state of the art for graph structured link prediction, especially when the side information are not available.

For the future work, we plan to investigate to propose a method for link prediction which can make use of the variety of information sources associated with graphs.

\begin{thebibliography}{4}

\bibitem{adamic} Adamic, L.A., and Eytan, A.: Friends and neighbors on the web. Social networks 25.3 (2003): 211-230.

\bibitem{katz} Katz, L.: A new status index derived from sociometric analysis. Psychometrika 18.1 (1953): 39-43.

\bibitem{lhni} Leicht, E.A., et al.: Vertex similarity in networks. Physical Review E 73.2 (2006): 026120.

\bibitem{pa}  Barabasi, A.L, Albert, R.: Emergence of Scaling in Random Networks, Science 286 (1999) 509.

\bibitem{matrix-factorization} Menon, A., and Charles, E.: Link prediction via matrix factorization. Machine Learning and Knowledge Discovery in Databases (2011): 437-452.

\bibitem{protein-protein} Von. M.C, et al.: Comparative assessment of large-scale data sets of protein–protein interactions. Nature 417.6887 (2002): 399-403.

\bibitem{metabolic} Yamanishi, Y., et al.: Supervised enzyme network inference from the integration of genomic data and chemical information. Bioinformatics 21.suppl-1 (2005): i468-i477.

\bibitem{nips} Rowies, S.: NIPS dataset (2002), http://www.cs.nyu.edu/~rwoeis/data.html

\bibitem{condmat} Lichtenwalter, R. N., et al.: New perspectives and methods in link prediction. Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010.

\bibitem{conflict1} Ghosn, F., et al.: The MID3 data set, 1993–2001: Procedures, coding rules, and description. Conflict Management and Peace Science 21.2 (2004): 133-154.

\bibitem{conflict2} Ward, M.D., et al.: Disputes, democracies, and dependencies: A reexamination of the Kantian peace. American Journal of Political Science 51.3 (2007): 583-601.

\bibitem{powergrid} Watts, D.J., and Steven, H.S.: Collective dynamics of ‘small-world’networks. nature 393.6684 (1998): 440-442.

\bibitem{nspdk} Costa, F, and Kurt, D.G.: Fast neighborhood subgraph pairwise distance kernel. Proceedings of the 26th International Conference on Machine Learning. Omnipress, 2010.

\bibitem{convolution-kernel} Haussler, D.: Convolution kernels on discrete structures. Vol. 646. Technical report, Department of Computer Science, University of California at Santa Cruz, 1999.

%\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
%Subsequences. J. Mol. Biol. 147, 195--197 (1981)
%
%\bibitem{lncschap} May, P., Ehrlich, H.C., Steinke, T.: ZIB Structure Prediction Pipeline:
%Composing a Complex Biological Workflow through Web Services. In: Nagel,
%W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006. LNCS, vol. 4128,
%pp. 1148--1158. Springer, Heidelberg (2006)
%
%\bibitem{book} Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing
%Infrastructure. Morgan Kaufmann, San Francisco (1999)
%
%\bibitem{proceeding1} Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid
%Information Services for Distributed Resource Sharing. In: 10th IEEE
%International Symposium on High Performance Distributed Computing, pp.
%181--184. IEEE Press, New York (2001)
%
%\bibitem{proceeding2} Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The Physiology of the
%Grid: an Open Grid Services Architecture for Distributed Systems
%Integration. Technical report, Global Grid Forum (2002)
%
%\bibitem{url} National Center for Biotechnology Information, \url{http://www.ncbi.nlm.nih.gov}

\end{thebibliography}

\end{document}

### 2017-06-29 paper.tex
Add files via upload

@@
 
-\section{Introduction}
+\section{Introduction and related work}
 A huge amount and variety of relational data are available in a wide range of fields.
@@
 Thus we the term link prediction methods to refer to topology-based link prediction methods.
+Conerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning.
 
-Conerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning.
 Unsupervised learning methods compute the scores for node couples based on topological features and directly use these scores to consider non-observed links to be present or absent.
-Typical examples link prediction methods which fall into this class are Adamic-Adar \cite{adamic}, Katz \cite{katz}, Leicht-Home-Newman \cite{lhni}, etc.
-Supervised learning link prediction methods are based on a learning process which try to separate present links and absent links by their characteristics.
-A link prediction method via matrix factorization \cite{matrix-factorization} is for instance.
+In \cite{adamic}, a method, \textit{Adamic-Adar}, is proposed in which a score between two nodes is computed by a weighted sum over their common nodes.
+Nodes with smaller degree are weighted more comparing to the higher ones.
+Another method also considers node degree when computing proximity is presented.
+The probability of a existing link connecting two nodes is proportional to the product of their node degrees.
+Different from the method in \cite{adamic} which considers the common nodes, a link prediction method, \textit{Katz}, is introduced in \cite{katz} that takes into acount the number of common paths with different lengths between two nodes to measure the proximity between them.
+The shorter paths are given more weights, meanwhile the longer ones are weighted less.
+Another method which is a modification of \textit{Katz} notated as Leicht-Holme-Newman is presented in \cite{lhni}.
+In this method the similarity of a node couple is based on an assumption that two nodes are more similar if they have more similar intermediate nodes.
+Besides, in \cite{matrix-factorization} they also apply a raw singular value decomposition, SVD, on the adjacency matrix for link prediction.
+Generally, unsupervised learning methods takes the advantage from their complexity since they do not face with learning process.
+However, in many case, they do not show impressing results.
+
+Supervised learning link prediction methods are based on a learning process which try to learn a curve that separates present links and absent links relied on their characteristics.
 This group of methods can also be further grouped into four subsets: feature-based models, graph regularization models, latent class models and latent feature models as presented in \cite{matrix-factorization}.
-For the performance, supervised methods tend to show better performance comparing to unsupervised ones in general.
+In \cite{nonparametric}, a nonparametric latent feature models for link prediction is introduced in which latent features are extracted by based on an adaptation of Bayesain nonparametric approach.
+Besides, this method is able to concurrently learn number of latent features and assign which entities have these features.
+Another method related to latent features is presented in \cite{matrix-factorization}, they propose to use matrix factorization to extract latent features.
+This method can also take the output of unsupervised methods as its input to proceed.
+They show impressive results with different use of loss functions: square loss function, log loss function.
+Compared to unsupervised learning methods, supervised methods tend to show better performance in general.
 However, they normally face with the high compexity in term of computation and memory consumption.
@@
 We consider a graph $G=(V,E)$ where $V$ is the set of nodes and $E$ is the set of links.
-The set $E$ can be devided into a subset of observed links (O) and a subset of unobserved links (U).
-The problem is that the set O is not a complete set.
+The set $E$ can be devided into a subset of observed links ($O$) and a subset of unobserved links ($U$).
+The problem is that the set $O$ is not a complete set.
 Therefore, \textit{link prediction} is the task that aims at exploiting graph structure to rank links in $U$ from the most to the least probable to be considered as observed links in $O$.
@@
 The values of $\lambda$ depend on the histogram of graph node degree.
-We can use tuning in order to obtain suitable value for $\lambda$.
+We can use tuning technique in order to obtain suitable value for $\lambda$.
 \subsection{Link representation}
-In this section, we propose a method to represent links in the form of neighborhood subgraphs.
+Most methods for link prediction attempt to computes similarities between nodes and consider to rank links.
+We desire to take links as examples to learn and predict.
+Therefore, we propse a method which model the context of two nodes to represent for link connecting them.
 
 Let us consider two nodes $u$ and $v$ ($u, v \in V$), we first extract two neighborhood subgraphs with radius $R$ rooted at $u$ and $v$ to obtain $N_R(u)$ and $N_R(v)$, respectively.
-We then represent a link connecting $u$ and $v$ by a graph $G_{uv}$ formed by taking a union of these two achieved subgraphs: $G_{uv}= N_R(u) \cup N_R(v)$.
+We then create an artificial node $w$.
+This node is connected to both $u$ and $v$.
+As a consequence, we achieve a single graph representing for a link connecting $u$ and $v$.
 \subsection{Joint neighborhood subgraphs link prediction}
@@
 
+\bibitem{nonparametric} Miller, K., Michael, et al.: Nonparametric latent feature models for link prediction. Advances in neural information processing systems. 2009.
+
 \bibitem{protein-protein} Von. M.C, et al.: Comparative assessment of large-scale data sets of protein–protein interactions. Nature 417.6887 (2002): 399-403.

### 2017-06-29 paper.tex
Add files via upload

@@
 The set $E$ can be devided into a subset of observed links ($O$) and a subset of unobserved links ($U$).
-The problem is that the set $O$ is not a complete set.
-Therefore, \textit{link prediction} is the task that aims at exploiting graph structure to rank links in $U$ from the most to the least probable to be considered as observed links in $O$.
+It is often that the set $O$ is not a complete set since they are many actual links are missing.
+Therefore, finding most likely set of links in $U$ to be considered as the complement set of $O$ is an important task which impacts on the performance of graph-based systems.
+Link prediction is the task that aims at exploiting graph structure to rank links in $U$ from the most to the least probable to be considered as observed links in $O$.
 
-The \textit{distance} between two nodes $u$ and $v$, notated as $\mathcal{D}(u,v)$, is the length of the shortest path between them.
-The \textit{neighborhood} with radius $r$ of a node $v$ is the set of nodes
-at a distance no greater than $r$ from $v$ and denoted by $N_r(v)$.
-The \textit{neighborhood subgraph} with radius $r$ of node $v$, denoted by $\mathcal{N}_{r}^{v}$,  is the subgraph formed by the nodes in the
-neighborhood with radius $r$ of $v$ and the relative edges with endpoints in $N_r(v)$. The degree of a node $u$ denoted as $d(u)$ is the number of its neighborhood $d(u) = \mathcal{N}_{1}^{u}$.
+We define the \textit{distance} between two nodes $u$ and $v$, notated as $\mathcal{D}(u,v)$, is the length of the shortest path between them.
+The \textit{neighborhood} of a node $u$ with radius $r$ is the set of nodes such that they are at distance no greater than $r$ from $u$ and it is denoted by $N_r(u)$ and $N_r(u) = \lbrace v\ |\ d(u,v) \leq r \rbrace$.
+The \textit{neighborhood subgraph} with radius $r$ of a given node $u$, denoted by $\mathcal{N}_{r}^{u}$, is the subgraph formed by the nodes in the
+\textit{neighborhood} with radius $r$ of $u$ and the relative edges with endpoints in $N_r(u)$.
+The degree of a node $u$ denoted as $d(u)$ is the cardinality of its neighborhood $d(u) = |\mathcal{N}_{1}^{u}|$.
 \subsection{The neighborhood subgraph pairwise distance kernel}
-The NSPDK \cite{nspdk} is an instance of convolution kernel \cite{convolution-kernel} where given a graph $G \in \mathcal{G}$ and two rooted graphs $A_u, B_v$, the relation $R_{r,d}(A_u, B_v, G)$ is true {\em iff} $A_u \cong \mathcal{N}_r^u$ is (up to isomorphism $\cong$) a neighborhood subgraph of radius $r$ of $G$ and so is $B_v \cong  \mathcal{N}_r^v$, with roots at distance $\mathcal{D}(u,v)= d$.
-We denote $R^{-1}$ as the inverse relation that returns all pairs of neighborhoods of radius $r$ at distance $d$ in $G$, $R^{-1}_{r,d}(G) = \lbrace A_u, B_v | R_{r,d}(A_u,B_v,G)=true\rbrace$.
-The kernel $\kappa_{r,d}$ over $\mathcal{G} \times \mathcal{G}$, counts the number of such fragments in common in two input graphs:
+In this section, we briefly desbribe an efficient kernel named NSPDK \cite{nspdk} which allows to measure the similarity between labeled graphs.
+NSPDK is an instance of decompositional kernel \cite{convolution-kernel}.
+
+Given a labeled graph $G \in \mathcal{G}$ and two rooted graphs $A_u, B_v$, we first define the relation $R_{r,d}(A_u, B_v, G)$ to be true {\em iff} $A_u \cong \mathcal{N}_r^u$ is (up to isomorphism $\cong$) a neighborhood subgraph with radius $r$ of $G$ and so is $B_v \cong  \mathcal{N}_r^v$, such that $v$ is a distance $d$ from $u$: $\mathcal{D}(u,v)= d$.
+We then define the inverse relation $R^{-1}$ that returns all pairs of neighborhoods of radius $r$ at distance $d$ in $G$, $R^{-1}_{r,d}(G) = \lbrace A_u, B_v | R_{r,d}(A_u,B_v,G)=true\rbrace$.
+The kernel $\kappa_{r,d}$ over $\mathcal{G} \times \mathcal{G}$ is the number of such fragments in common in two input graphs:
 \begin{center}
@@
 \end{center}
-\noindent where $\textbf{1}_{A \cong B}$ is the \textit{exact matching function} that returns 1 if $A$ is
-isomorphic to $B$ and 0 otherwise.
+\noindent where $\textbf{1}_{A \cong B}$ is the \textit{exact matching function} that returns 1 if $A$ is isomorphic to $B$ and 0 otherwise.
 Finally, the NSPDK is defined as $K(G,G') = \sum\limits_{r}{\sum\limits_{d}{\kappa_{r,d}(G,G')}}$, where for efficiency reasons, the values of $r$ and $d$ are upper bounded to a given maximal $r^*$ and $d^*$, respectively.
+
+Related to exact matching function, this function needs to solve the graph isomorphism problem.
+This problem is not known to be solvable in polynomial time nor to be NP-complete.
+In \cite{nspdk}, they propose an approximate method to figure out graph isomorphism problem.
+It first transforms graphs into strings.
+It then employ a hash function to map each unique string with an integer number.
+Finally, two graphs are isomorphic if they have the same corresponding integer numbers.
 
@@
 
-\item \textit{Metabolic} \cite{metabolic}: a biological network which relates enzyme proteins and chemical compounds and includes 668 nodes and 2782 links.
+\item \textit{Metabolic} \cite{metabolic}: a biological network which relates enzyme proteins and chemical compounds and it includes 668 nodes and 2782 links.
 
-\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference containing 2865 nodes and 4733 links.
+\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference from first to twelfth edition.
+Nodes are authors and links encode co-author relation between authors.
+This network contains 2865 nodes and 4733 links.
 
@@
 
-\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: a network describing the dispute between countries. It consists of 130 nodes and 180 links.
+\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: a network describing the dispute between 130 countries.
+A link connecting two nodes (countries) if they dispute.
+We have 180 links in total in this network.
 
@@
 Fact+Scores & 79.3$\pm$0.5 & 69.6$\pm$0.2 & 61.3$\pm$1.9 & 81.2$\pm$2.0 & 68.9$\pm$4.2 & 75.1$\pm$2.0 \\
-JNSL & 80.1$\pm$0.8 & 72.5$\pm$0.7 & 62.1$\pm$0.8 & 88.6$\pm$2.3 & 72.0$\pm$0.9 & 75.6$\pm$0.7 \\
+JNSL & \textbf{80.1$\pm$0.8} & \textbf{72.5$\pm$0.7} & \textbf{62.1$\pm$0.8} & \textbf{88.6$\pm$2.3} & \textbf{72.0$\pm$0.9} & \textbf{75.6$\pm$0.7} \\
  \hline 

### 2017-06-30 paper.tex
Add files via upload

@@
 The degree of a node $u$ denoted as $d(u)$ is the cardinality of its neighborhood $d(u) = |\mathcal{N}_{1}^{u}|$.
+We also notate the maximum node degree in the graph $G$ as $d(G)$, $d(G) = max\lbrace d(u)\ |\ u \in V \rbrace$
 \subsection{The neighborhood subgraph pairwise distance kernel}
@@
 Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure.
-Here, we propose to use node labeling fuctions $L$ that take into account node degrees for their labels such that $\ell(u) = \ell(v)$ if $|d(u) - d(v)|\leq \lambda$, in which $\lambda$ is a hyper parameter.
+Here, we propose to a node labeling fuction $\ell$ such that nodes with similar degrees are assigned the same label.
 It is due to the assumption that nodes with similar degrees tend to share common properties.
+Following is the definition of the the function:
+\begin{center}
+$\ell(u) = \left\{
+	\begin{array}{ll}
+		d(u),\  & \mbox{if } d(u) \leq 5 \\
+		6+i,\ & \mbox{if }  5 + \frac{d(G) - 5}{\lambda-5}*i \leq d(u) < 5 + \frac{d(G) - 5}{\lambda-5}*(i+1)
+	\end{array}
+\right.$,
+\end{center}
+where $\lambda > 5$ is the number of labels used to label for nodes in the graphs.
 The values of $\lambda$ depend on the histogram of graph node degree.
@@
 \textbf{Model Selection}: The values of different hyper-parameters are set by using a 3-fold on training set in which we use one fold for training and the rest two folds for validation.
-We tune the values of radius for extracting subgraphs $R$ in $\lbrace 1, 2 \rbrace$, $\lambda$ for node degree function in $\lbrace 1, 2 \rbrace$, for $r$ and $d$ parameters of NSPDK in $\lbrace  1, 2 \rbrace$ and $\lbrace  1, 2, 3 \rbrace$, respectively.
+We tune the values of radius for extracting subgraphs $R$ in $\lbrace 1, 2 \rbrace$, $\lambda$ in node label function in $\lbrace 10, 15 \rbrace$, for $r$ and $d$ parameters of NSPDK in $\lbrace  1, 2 \rbrace$ and $\lbrace  1, 2, 3 \rbrace$, respectively.
 Finally, the regularization tradeoff $C$ for the SVM is picked up in $\lbrace 10^{-4}, 10^{-3}, 10^{-2},\ 10^{-1}, 1,\ 10,\ 10^2, 10^3,\ 10^4 \rbrace$.
@@
 \section{Results and Discussion}
-Table \ref{result_table} shows the performance of link prediction methods in ROC-AUC on six datasets.
+Table \ref{result_table} shows the performance of link prediction methods in ROC-AUC on six datasets in which we mark as bold for the best ROC-AUC on each dataset.
 From the results on the table, we can group methods into two groups based on their performances: supervised methods and unsupervised methods.
@@
 \begin{table}
-\caption{The performance in percentage on six datasets of different link prediction methods in which AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top: Liear regression running on unsupervised scores \cite{matrix-factorization}:, SVD \cite{matrix-factorization}:: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores.
+\caption{The ROC-AUC performance on six datasets of different link prediction methods in which AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top: Liear regression running on unsupervised scores \cite{matrix-factorization}:, SVD \cite{matrix-factorization}:: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores.
 }
@@
 \textbf{Methods} & Protein & Metabolic & Nips & Condmat & Conflict & PowerGrid\\
+	& ($\%$) & ($\%$) & ($\%$) & ($\%$) & ($\%$) & ($\%$)\\
 \hline

### 2017-06-30 paper.tex
Update .tex and pdf file
F

@@
 Graphs are common data structure used to represent data in which the relation between entities are encoded.
-A number of graph-based methods and systems have been proposed, varying from biology to recomendation to social network.
+A number of graph-based methods and systems have been proposed, varying from biology to recommendation to social network.
 Most methods have to take partially observed graphs as the input to proceed due to the lack of information.
-This prevents them from showing promissing results.
+This prevents them from showing promising results.
 Link prediction becomes an effective paradigm to solve this problem.
@@
 We then employ a decompositional graph kernel to measure the similarity between links.
-An empirical experiment on diferent datasets proves that our proposed method shows the state of the art for link prediction.
+An empirical experiment on different datasets proves that our proposed method shows the state of the art for link prediction.
 \keywords{Link prediction, joint neighborhood subgraphs}
@@
 On the other hand, it raises challenges for machine learning and data scientists to design high performance predictive systems.
-A common data struture for representing relational data is graph whose nodes describe for entities and links depict their relations.
+A common data structure for representing relational data is graph whose nodes describe for entities and links depict their relations.
 We can easily see graph-based systems in different domains like biology, chemistry or networking.
@@
 As a consequence, many link prediction methods have been proposed with the aim of recovering the missing links.
-A graph could be associtated with external information sources, so called "side information".
+A graph could be associated with external information sources, so called "side information".
 Therefore, a link prediction method attempts to exploit the graph topology and side information to build a the model for predicting the presence or absence of link any between couple of nodes.
@@
 Thus we the term link prediction methods to refer to topology-based link prediction methods.
-Conerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning.
+Concerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning.
 
@@
 The probability of a existing link connecting two nodes is proportional to the product of their node degrees.
-Different from the method in \cite{adamic} which considers the common nodes, a link prediction method, \textit{Katz}, is introduced in \cite{katz} that takes into acount the number of common paths with different lengths between two nodes to measure the proximity between them.
+Different from the method in \cite{adamic} which considers the common nodes, a link prediction method, \textit{Katz}, is introduced in \cite{katz} that takes into account the number of common paths with different lengths between two nodes to measure the proximity between them.
 The shorter paths are given more weights, meanwhile the longer ones are weighted less.
@@
 Compared to unsupervised learning methods, supervised methods tend to show better performance in general.
-However, they normally face with the high compexity in term of computation and memory consumption.
+However, they normally face with the high complexity in term of computation and memory consumption.
 
@@
 We consider a graph $G=(V,E)$ where $V$ is the set of nodes and $E$ is the set of links.
-The set $E$ can be devided into a subset of observed links ($O$) and a subset of unobserved links ($U$).
+The set $E$ can be divided into a subset of observed links ($O$) and a subset of unobserved links ($U$).
 It is often that the set $O$ is not a complete set since they are many actual links are missing.
@@
 The \textit{neighborhood subgraph} with radius $r$ of a given node $u$, denoted by $\mathcal{N}_{r}^{u}$, is the subgraph formed by the nodes in the
-\textit{neighborhood} with radius $r$ of $u$ and the relative edges with endpoints in $N_r(u)$.
+\textit{neighborhood} with radius $r$ of $u$ and the corresponding edges with endpoints in $N_r(u)$.
 The degree of a node $u$ denoted as $d(u)$ is the cardinality of its neighborhood $d(u) = |\mathcal{N}_{1}^{u}|$.
@@
 Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure.
-Here, we propose to a node labeling fuction $\ell$ such that nodes with similar degrees are assigned the same label.
+Here, we propose to a node labeling function $\ell$ such that nodes with similar degrees are assigned the same label.
 It is due to the assumption that nodes with similar degrees tend to share common properties.
@@
 We desire to take links as examples to learn and predict.
-Therefore, we propse a method which model the context of two nodes to represent for link connecting them.
+Therefore, we propose a method which model the context of two nodes to represent for link connecting them.
 
@@
 In this section, we intend to measure the performance of our proposed method and compare it with other link prediction methods.
-We follow the procedure used in \cite{matrix-factorization} which employs six datasets in different fields.
-Following, we give each dataset a short description.
+We follow the procedure used in \cite{matrix-factorization} which employs six datasets in different domains.
+In the following we shortly describe each dataset.
 \begin{itemize}
@@
 
-\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference from first to twelfth edition.
+\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference from the first to the $12^{th}$ edition.
 Nodes are authors and links encode co-author relation between authors.

### 2017-06-30 paper.tex
F

@@
 \section{Introduction and related work}
+We are witnessing a constant increase of the rate at which data is being produced and made available in machine readable formats.
+Interestingly it is not only the quantity of data that is increasing, but also its complexity, i.e.
+not only are we measuring a number of attributes or features for each data point, but we are also capturing their mutual relationships, that is, we are considering data that is non independent and identically distributed (non i.i.d.).
+This yields collections that are best represented as graphs or relational data bases and requires a more complex form of analysis.
+
 A huge amount and variety of relational data are available in a wide range of fields.
@@
 		d(u),\  & \mbox{if } d(u) \leq 5 \\
-		6+i,\ & \mbox{if }  5 + \frac{d(G) - 5}{\lambda-5}*i \leq d(u) < 5 + \frac{d(G) - 5}{\lambda-5}*(i+1)
+		6+i,\ & \mbox{if }  5 + \left[ \frac{d(G) - 5}{\lambda-5} \right] *i \leq d(u) < 5 + \left[ \frac{d(G) - 5}{\lambda-5}\right] *(i+1)
 	\end{array}
@@
 where $\lambda > 5$ is the number of labels used to label for nodes in the graphs.
-The values of $\lambda$ depend on the histogram of graph node degree.
+The value of $\lambda$ depend on the histogram of graph node degree.
 We can use tuning technique in order to obtain suitable value for $\lambda$.
@@
 The difference between their performance is small in PowerGrid and Protein datasets with 0.5$\%$ and 0.8$\%$, respectively.
+And the big gap is in the Condmat dataset with 7.4$\%$.
 

### 2017-06-30 paper.tex
F

@@
 Interestingly it is not only the quantity of data that is increasing, but also its complexity, i.e.
-not only are we measuring a number of attributes or features for each data point, but we are also capturing their mutual relationships, that is, we are considering data that is non independent and identically distributed (non i.i.d.).
+not only are we measuring a number of attributes or features for each data point, but we are also capturing their mutual relationships, that is, we are considering non independent and identically distributed (non i.i.d.) data.
 This yields collections that are best represented as graphs or relational data bases and requires a more complex form of analysis.
+As cursory examples of domains of interest  it is sufficient to mention social networks, where nodes are people and edges encode a type of association such as friendship, bioinformatics, where nodes are proteins or metabolites and edges represent the type of chemical interaction,
 

### 2017-06-30 paper.tex
F

@@
 This yields collections that are best represented as graphs or relational data bases and requires a more complex form of analysis.
-As cursory examples of domains of interest  it is sufficient to mention social networks, where nodes are people and edges encode a type of association such as friendship, bioinformatics, where nodes are proteins or metabolites and edges represent the type of chemical interaction,
+As cursory examples of application domains that are particularly  it is sufficient to mention social networks, where nodes are people and edges encode a type of association such as friendship or co-authorship, bioinformatics, where nodes are proteins and metabolites and edges represent a type of chemical interaction such as catalysis or signaling, and e-commerce, where nodes are people and goods and edges encode a ''buy'' or ''like'' relationship.
 
-A huge amount and variety of relational data are available in a wide range of fields.
-On the one hand, it provides an opportunity to build systems which automatically extract useful information.
-On the other hand, it raises challenges for machine learning and data scientists to design high performance predictive systems.
-A common data structure for representing relational data is graph whose nodes describe for entities and links depict their relations.
-We can easily see graph-based systems in different domains like biology, chemistry or networking.
-These systems require the data form used for their input as graphs.
 However, despite the availability of huge data, most graphs are only partially observed graphs.

### 2017-06-30 paper.tex
F

@@
 As cursory examples of application domains that are particularly  it is sufficient to mention social networks, where nodes are people and edges encode a type of association such as friendship or co-authorship, bioinformatics, where nodes are proteins and metabolites and edges represent a type of chemical interaction such as catalysis or signaling, and e-commerce, where nodes are people and goods and edges encode a ''buy'' or ''like'' relationship.
+A key characteristic of this type of data collections is the sparseness and dynamic nature, i.e.
+the fact that the number of recorded relations is significantly smaller than the number of all possible pairwise relations, and the fact that these relations evolve in time.
+A crucial computational task is then the ''link prediction problem'' which allows to suggest friends, or possible collaborators for scientists in social networks, or to discover unknown interactions between proteins to explain the mechanism of a disease, or to suggest novel products to be bought to a customer.
 
-However, despite the availability of huge data, most graphs are only partially observed graphs.
-That means a number of actual links in each graph are absent or missing.
-Tackling this issue is a necessary condition to obtain high performance graph-based predictive systems.
 As a consequence, many link prediction methods have been proposed with the aim of recovering the missing links.

### 2017-06-30 paper.tex
Add average node degree
revise node labeling

@@
 Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure.
-Here, we propose to a node labeling function $\ell$ such that nodes with similar degrees are assigned the same label.
-It is due to the assumption that nodes with similar degrees tend to share common properties.
-Following is the definition of the the function:
+Here, we propose to a node labeling function $\ell$ which assigns labels for nodes based on node degrees.
+Our idea is that nodes having small degree, less than or equal to 5, we use the degree values as their labels.
+For nodes with degree greater than 5, we group them into different groups based on the degrees, nodes are in the same group are assigned the same labels.
+We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties.
+Formally, the function is defined as:
 \begin{center}
@@
 \begin{itemize}
-\item \textit{Protein }\cite{protein-protein}: the medium confidence network which encodes the interaction between proteins. It contains 2617 nodes and 11855 links.
+\item \textit{Protein }\cite{protein-protein}: the medium confidence network which encodes the interaction between proteins. It contains 2617 nodes and 11855 links. The average degree is 9.1.
 
-\item \textit{Metabolic} \cite{metabolic}: a biological network which relates enzyme proteins and chemical compounds and it includes 668 nodes and 2782 links.
+\item \textit{Metabolic} \cite{metabolic}: a biological network which relates enzyme proteins and chemical compounds and it includes 668 nodes and 2782 links. The average degree is 8.3.
 
@@
 This network contains 2865 nodes and 4733 links.
+The average degree is 3.3.
 
-\item \textit{Condmat} \cite{condmat}: a network of co-authors for condensed matter physists. This network has 14230 nodes and 1196 links.
+\item \textit{Condmat} \cite{condmat}: a network of co-authors for condensed matter physists. This network has 14230 nodes and 1196 links. The average degree is 0.17.
 
@@
 We have 180 links in total in this network.
+The average degree is 2.5.
 
-\item \textit{Powergrid} cite{powergrid}: a network of electric powergrid in US. It has 4941 nodes and 6594 links.
+\item \textit{Powergrid} cite{powergrid}: a network of electric powergrid in US. It has 4941 nodes and 6594 links. The average degree is 2.7.
 \end{itemize}

### 2017-06-30 paper.tex
F

--- 2017-06-30 paper.tex
@@
 the fact that the number of recorded relations is significantly smaller than the number of all possible pairwise relations, and the fact that these relations evolve in time.
-A crucial computational task is then the ''link prediction problem'' which allows to suggest friends, or possible collaborators for scientists in social networks, or to discover unknown interactions between proteins to explain the mechanism of a disease, or to suggest novel products to be bought to a customer.
+A crucial computational task is then the ''link prediction problem'' which allows to suggest friends, or possible collaborators for scientists in social networks, or to discover unknown interactions between proteins to explain the mechanism of a disease in biological networks, or to suggest novel products to be bought to a customer in a e-commerce recommendation system.
+The many approaches to link prediction that exist in literature can be partitioned according to 1) whether additional or ''side'' information is available for nodes and edges or rather only the network topology is considered and 2) whether the approach is unsupervised or supervised.
 

### 2017-06-30 paper.tex
F

@@
 
-As a consequence, many link prediction methods have been proposed with the aim of recovering the missing links.
-A graph could be associated with external information sources, so called "side information".
-Therefore, a link prediction method attempts to exploit the graph topology and side information to build a the model for predicting the presence or absence of link any between couple of nodes.
-An expected method is required to make use of both such kind of data sources.
-In this paper, we only focus on the topological information.
-Thus we the term link prediction methods to refer to topology-based link prediction methods.
-Concerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning.
-
-Unsupervised learning methods compute the scores for node couples based on topological features and directly use these scores to consider non-observed links to be present or absent.
-In \cite{adamic}, a method, \textit{Adamic-Adar}, is proposed in which a score between two nodes is computed by a weighted sum over their common nodes.
-Nodes with smaller degree are weighted more comparing to the higher ones.
-Another method also considers node degree when computing proximity is presented.
-The probability of a existing link connecting two nodes is proportional to the product of their node degrees.
-Different from the method in \cite{adamic} which considers the common nodes, a link prediction method, \textit{Katz}, is introduced in \cite{katz} that takes into account the number of common paths with different lengths between two nodes to measure the proximity between them.
-The shorter paths are given more weights, meanwhile the longer ones are weighted less.
-Another method which is a modification of \textit{Katz} notated as Leicht-Holme-Newman is presented in \cite{lhni}.
-In this method the similarity of a node couple is based on an assumption that two nodes are more similar if they have more similar intermediate nodes.
-Besides, in \cite{matrix-factorization} they also apply a raw singular value decomposition, SVD, on the adjacency matrix for link prediction.
-Generally, unsupervised learning methods takes the advantage from their complexity since they do not face with learning process.
-However, in many case, they do not show impressing results.
+Unsupervised learning methods are non-adaptive, and hence computationally efficient, and define a score for any node pair that is proportional to the existence likelihood of an edge between the two nodes.
+\textit{Adamic-Adar} \cite{adamic} computes the weighted sum over the common neighbors where the weight is inversely proportional to the (log of) each neighbor node degree.
+The \textit{preferential attachment} method computes a score simply as the product of the node degrees in an attempt to exploit the 'rich get richer' property of certain network dynamics.
+\textit{Katz} \cite{katz} takes into account the number of common paths with different lengths between two nodes, assigning more weight to shorter paths.
+The \textit{Leicht-Holme-Newman} method \cite{lhni} computes the number of intermediate nodes.
+In \cite{matrix-factorization} the score is derived from the singular value decomposition of the adjacency matrix.
 
@@
 However, they normally face with the high complexity in term of computation and memory consumption.
+
+In this work we present a novel supervised approach based on pure topological information.
 

### 2017-06-30 paper.tex
Change node labeling

@@
 Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure.
-Here, we propose to a node labeling function $\ell$ which assigns labels for nodes based on node degrees.
-Our idea is that nodes having small degree, less than or equal to 5, we use the degree values as their labels.
-For nodes with degree greater than 5, we group them into different groups based on the degrees, nodes are in the same group are assigned the same labels.
+Here, we propose a node labeling function $\ell$ which assigns labels for nodes based on node degrees.
+First, we use the degree values for their labels for nodes having degree less than or equal 5.
+We then discretize the degrees larger than 5 into k bins and assign the same label for nodes belong to the same bin.
 We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties.
@@
 		d(u),\  & \mbox{if } d(u) \leq 5 \\
-		6+i,\ & \mbox{if }  5 + \left[ \frac{d(G) - 5}{\lambda-5} \right] *i \leq d(u) < 5 + \left[ \frac{d(G) - 5}{\lambda-5}\right] *(i+1)
+		5+i,\ & \mbox{if } d(u) > 5
 	\end{array}
@@
 \end{center}
-where $\lambda > 5$ is the number of labels used to label for nodes in the graphs.
+where $i = \lceil \frac{d(u)-5}{bin}\rceil$, $bin = \frac{d(G)-5}{\lambda - 5}$ and $\lambda$ ($\lambda > 5$) is the number of labels used to label for nodes in the graphs.
 The value of $\lambda$ depend on the histogram of graph node degree.

### 2017-06-30 paper.tex
F

--- 2017-06-30 paper.tex
@@
 
-Supervised learning link prediction methods are based on a learning process which try to learn a curve that separates present links and absent links relied on their characteristics.
-This group of methods can also be further grouped into four subsets: feature-based models, graph regularization models, latent class models and latent feature models as presented in \cite{matrix-factorization}.
-In \cite{nonparametric}, a nonparametric latent feature models for link prediction is introduced in which latent features are extracted by based on an adaptation of Bayesain nonparametric approach.
-Besides, this method is able to concurrently learn number of latent features and assign which entities have these features.
-Another method related to latent features is presented in \cite{matrix-factorization}, they propose to use matrix factorization to extract latent features.
-This method can also take the output of unsupervised methods as its input to proceed.
-They show impressive results with different use of loss functions: square loss function, log loss function.
-Compared to unsupervised learning methods, supervised methods tend to show better performance in general.
-However, they normally face with the high complexity in term of computation and memory consumption.
+Supervised link prediction methods convert the problem into a binary classification task where links present in the network (at a given time) are considered as positive instances and a subset of all the non links are considered as negative instances.
+Following \cite{matrix-factorization}, we can further group these methods into four classes: feature-based models, graph regularization models, latent class models and latent feature models.
+A Bayesian nonparametric approach is used in \cite{nonparametric} to compute a nonparametric latent feature model that does not need a user defined number of latent features but rather induces it as part of the training phase.
+In \cite{matrix-factorization} a matrix factorization approach is used to extract latent features that can take into consideration the output of an unsupervised method.
+The authors show impressive increase in predictive performance when considering a ranking loss function to deal with the imbalance problem (i.e.
+a much larger number of negative vs positive instances).
 
-In this work we present a novel supervised approach based on pure topological information.
+In general supervised methods exhibit better accuracies compared to unsupervised methods although incurring in much higher computational and memory complexity costs.
 
@@
 It then adopts a decompositional graph kernel which allow to fully exploit graphs' structure to measure the similarity, one of the key point in machine learning algorithms.
+
+In this work we present a novel supervised approach based on pure topological information.
+The main contribution is
 

### 2017-06-30 paper.tex
F

@@
 First, we use the degree values for their labels for nodes having degree less than or equal 5.
-We then discretize the degrees larger than 5 into k bins and assign the same label for nodes belong to the same bin.
+We then discretize the degrees larger than a user defined threshold $T$ ($T=5$ in our experimental evaluation) into $k$ bins and assign the same label for nodes belong to the same bin.
 We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties.
@@
 	\begin{array}{ll}
-		d(u),\  & \mbox{if } d(u) \leq 5 \\
-		5+i,\ & \mbox{if } d(u) > 5
+		d(u),\  & \mbox{if } d(u) \leq T \\
+		T+i,\ & \mbox{if } d(u) > T
 	\end{array}
@@
 \end{center}
-where $i = \lceil \frac{d(u)-5}{bin}\rceil$, $bin = \frac{d(G)-5}{\lambda - 5}$ and $\lambda$ ($\lambda > 5$) is the number of labels used to label for nodes in the graphs.
+where $i = \lceil \frac{d(u)-T}{bin}\rceil$, $bin = \frac{d(G)-T}{\lambda - T}$ and $\lambda$ ($\lambda > T$) is the number of labels used to label for nodes in the graphs.
 The value of $\lambda$ depend on the histogram of graph node degree.

### 2017-06-30 paper.tex
F

@@
 A Bayesian nonparametric approach is used in \cite{nonparametric} to compute a nonparametric latent feature model that does not need a user defined number of latent features but rather induces it as part of the training phase.
-In \cite{matrix-factorization} a matrix factorization approach is used to extract latent features that can take into consideration the output of an unsupervised method.
-The authors show impressive increase in predictive performance when considering a ranking loss function to deal with the imbalance problem (i.e.
-a much larger number of negative vs positive instances).
+In \cite{matrix-factorization} a matrix factorization approach is used to extract latent features that can take into consideration the output of an arbitrary unsupervised method.
+The authors show a significant increase in predictive performance when considering a ranking loss function suitable for  the imbalance problem, i.e.
+when the number of negative is much larger than the number of positive instances.
 

### 2017-06-30 paper.tex
F

@@
 In general supervised methods exhibit better accuracies compared to unsupervised methods although incurring in much higher computational and memory complexity costs.
-
-The common feature of most existing supervised and unsupervised methods for link prediction is that they use transitive manner to exploit the graph structure.
-This manner normally does not show high discriminative capacity.
-Therefore, in this paper, we propose a novel supervised method named joint neighborhood subgraphs link prediction (JNSL).
-Our method first introduces a method to represent each link between two nodes as a graph composed by taking a union of neighborhood subgraphs rooted at these these corresponding nodes.
-It then adopts a decompositional graph kernel which allow to fully exploit graphs' structure to measure the similarity, one of the key point in machine learning algorithms.
-
-In this work we present a novel supervised approach based on pure topological information.
-The main contribution is
+Moreover, most approaches implicitly represent the link prediction problem and the inference used to tackle it as a disjunction over the edges, that is, information on edges is propagated in an additive fashion so that for a node to have $k$ neighbors or $k+1$ does not make a drastic difference.
+We claim that this hypothesis is likely putting a cap on the discriminative power of classifiers and therefore we propose a novel supervised method that employs a conjunctive representation.
+We call the method ''joint neighborhood subgraphs link prediction'' (JNSL).
+The key idea here is to transform the link prediction task into a binary classification on suitable small subgraphs which we then solve using an efficient graph kernel method.
 
 \section{Method}
-In this section, we describe our proposed link prediction method which is based on the graph structure exploitation only.
+
 \subsection{Definitions and notation}
-We consider a graph $G=(V,E)$ where $V$ is the set of nodes and $E$ is the set of links.
-The set $E$ can be divided into a subset of observed links ($O$) and a subset of unobserved links ($U$).
-It is often that the set $O$ is not a complete set since they are many actual links are missing.
-Therefore, finding most likely set of links in $U$ to be considered as the complement set of $O$ is an important task which impacts on the performance of graph-based systems.
-Link prediction is the task that aims at exploiting graph structure to rank links in $U$ from the most to the least probable to be considered as observed links in $O$.
+We represent a problem instance as a graph $G=(V,E)$ where $V$ is the set of nodes and $E$ is the set of links.
+The set $E$ is partitioned into the subset of observed links ($O$) and the subset of unobserved links ($U$).
+Like other approaches we assume that all unobserved links are indeed ''non-links'' and we therefore define the link prediction problem as the task of ranking candidate links from the most to the least probable to recover links in $O$ but not in $U$ exploiting only the network topology.
 
-We define the \textit{distance} between two nodes $u$ and $v$, notated as $\mathcal{D}(u,v)$, is the length of the shortest path between them.
-The \textit{neighborhood} of a node $u$ with radius $r$ is the set of nodes such that they are at distance no greater than $r$ from $u$ and it is denoted by $N_r(u)$ and $N_r(u) = \lbrace v\ |\ d(u,v) \leq r \rbrace$.
-The \textit{neighborhood subgraph} with radius $r$ of a given node $u$, denoted by $\mathcal{N}_{r}^{u}$, is the subgraph formed by the nodes in the
-\textit{neighborhood} with radius $r$ of $u$ and the corresponding edges with endpoints in $N_r(u)$.
-The degree of a node $u$ denoted as $d(u)$ is the cardinality of its neighborhood $d(u) = |\mathcal{N}_{1}^{u}|$.
-We also notate the maximum node degree in the graph $G$ as $d(G)$, $d(G) = max\lbrace d(u)\ |\ u \in V \rbrace$
+We define the \textit{distance} $\mathcal{D}(u,v)$ between two nodes $u$ and $v$, as the number of edges on the shortest path between them.
+The \textit{neighborhood} of a node $u$ with radius $r$, $N_r(u) = \lbrace v\ |\ d(u,v) \leq r \rbrace$, is the set of nodes at distance no greater than $r$ from $u$.
+The corresponding \textit{neighborhood subgraph} $\mathcal{N}_{r}^{u}$ is the  subgraph induced by the neighborhood (i.e.
+considering all the edges with endpoints in $N_r(u)$).
+The \textit{degree} of a node $u$, $d(u) = |\mathcal{N}_{1}^{u}|$, is the cardinality of its neighborhood.
+The maximum node degree in the graph $G$ is $d(G)$.
+
 \subsection{The neighborhood subgraph pairwise distance kernel}

### 2017-06-30 paper.tex
F

@@
 
+\subsection{Link encoding as subgraphs union}
+Most methods for link prediction compute pairwise nodes similarities treating  the nodes defining the candidate edge independently.
+Instead we propose to jointly consider both candidate endpoint nodes together with their extended ''context''.
+To do so we build a graph starting from the two nodes and the underlying network.
+Given nodes $u$ and $v$, we first extract the two neighborhood sets with a user defined radius $R$ rooted at $u$ and $v$ to obtain $N_R(u)$ and $N_R(v)$, respectively.
+We then consider the graph $\mathcal{J}$ induced by the set union $N_R(u) \cup N_R(u)$.
+Finally we add an auxiliary node $w$ and the necessary edges to connect it to $u$ and $v$ (see Fig.\ref{key}).
+
+\subsection{Node labeling}
+We propose to use a graph kernel approach to classify the subgraphs encoding each link.
+In our setup nodes are not endowed with any ''side'' information.
+However to increase the discriminative power of the similarity notion induced by the graph kernel, instead of assuming a dummy, non-informative label on each node, we propose to use a node labeling function $\ell$ which assigns a discrete label as the node degree.
+As the degree distribution can in principle extend to large values, we employ a  discretization technique.
+First, we use the degree values for their labels for nodes having degree less than or equal 5.
+We then discretize the degrees larger than a user defined threshold $T$ ($T=5$ in our experimental evaluation) into $k$ bins and assign the same label for nodes belong to the same bin.
+We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties.
+Formally, the function is defined as:
+\begin{center}
+$\ell(u) = \left\{
+	\begin{array}{ll}
+		d(u),\  & \mbox{if } d(u) \leq T \\
+		T+i,\ & \mbox{if } d(u) > T
+	\end{array}
+\right.$,
+\end{center}
+where $i = \lceil \frac{d(u)-T}{bin}\rceil$, $bin = \frac{d(G)-T}{\lambda - T}$ and $\lambda$ ($\lambda > T$) is the number of labels used to label for nodes in the graphs.
+The value of $\lambda$ depend on the histogram of graph node degree.
+We can use tuning technique in order to obtain suitable value for $\lambda$.
+
 \subsection{The neighborhood subgraph pairwise distance kernel}
@@
 
-\subsection{Node labeling}
-NSPDK takes labeled graphs as its input to proceed.
-Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure.
-Here, we propose a node labeling function $\ell$ which assigns labels for nodes based on node degrees.
-First, we use the degree values for their labels for nodes having degree less than or equal 5.
-We then discretize the degrees larger than a user defined threshold $T$ ($T=5$ in our experimental evaluation) into $k$ bins and assign the same label for nodes belong to the same bin.
-We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties.
-Formally, the function is defined as:
-\begin{center}
-$\ell(u) = \left\{
-	\begin{array}{ll}
-		d(u),\  & \mbox{if } d(u) \leq T \\
-		T+i,\ & \mbox{if } d(u) > T
-	\end{array}
-\right.$,
-\end{center}
-where $i = \lceil \frac{d(u)-T}{bin}\rceil$, $bin = \frac{d(G)-T}{\lambda - T}$ and $\lambda$ ($\lambda > T$) is the number of labels used to label for nodes in the graphs.
-The value of $\lambda$ depend on the histogram of graph node degree.
-We can use tuning technique in order to obtain suitable value for $\lambda$.
-\subsection{Link representation}
-Most methods for link prediction attempt to computes similarities between nodes and consider to rank links.
-We desire to take links as examples to learn and predict.
-Therefore, we propose a method which model the context of two nodes to represent for link connecting them.
-
-Let us consider two nodes $u$ and $v$ ($u, v \in V$), we first extract two neighborhood subgraphs with radius $R$ rooted at $u$ and $v$ to obtain $N_R(u)$ and $N_R(v)$, respectively.
-We then create an artificial node $w$.
-This node is connected to both $u$ and $v$.
-As a consequence, we achieve a single graph representing for a link connecting $u$ and $v$.
 \subsection{Joint neighborhood subgraphs link prediction}

### 2017-06-30 paper.tex
F

@@
 In our setup nodes are not endowed with any ''side'' information.
-However to increase the discriminative power of the similarity notion induced by the graph kernel, instead of assuming a dummy, non-informative label on each node, we propose to use a node labeling function $\ell$ which assigns a discrete label as the node degree.
-As the degree distribution can in principle extend to large values, we employ a  discretization technique.
-First, we use the degree values for their labels for nodes having degree less than or equal 5.
-We then discretize the degrees larger than a user defined threshold $T$ ($T=5$ in our experimental evaluation) into $k$ bins and assign the same label for nodes belong to the same bin.
-We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties.
-Formally, the function is defined as:
+However to increase the discriminative power of the similarity notion induced by the graph kernel, instead of assuming a dummy, non-informative label on each node, we propose to use a node labeling function $\ell$ which assigns as the discrete label the node degree.
+More precisely, for nodes having degree less than or equal than a user defined threshold $T$ ($T=5$ in our experimental evaluation) we use as label the degree value.
+Degree values larger than $T$ are subsequently discretized into $k$ levels.
+Here the implicit assumption is that nodes with similar degrees have common properties.
+Formally, the labeling function is defined as:
 \begin{center}
@@
 \end{center}
-where $i = \lceil \frac{d(u)-T}{bin}\rceil$, $bin = \frac{d(G)-T}{\lambda - T}$ and $\lambda$ ($\lambda > T$) is the number of labels used to label for nodes in the graphs.
-The value of $\lambda$ depend on the histogram of graph node degree.
-We can use tuning technique in order to obtain suitable value for $\lambda$.
+where $i = \lceil \frac{d(u)-T}{bin}\rceil$, $bin = \frac{d(G)-T}{\lambda - T}$ and $\lambda$ ($\lambda > T$) is the maximum number of symbols used.
+The value of $\lambda$ depend on the degree distribution and can be tuned as a hyperparameter of the approach.
 
-\subsection{The neighborhood subgraph pairwise distance kernel}
-In this section, we briefly desbribe an efficient kernel named NSPDK \cite{nspdk} which allows to measure the similarity between labeled graphs.
-NSPDK is an instance of decompositional kernel \cite{convolution-kernel}.
+\subsection{The graph kernel}
+Here we briefly describe an efficient graph kernel called the Neighborhood Subgraph Pairs Distance kernel (NSPDK) introduced in \cite{nspdk}.
+NSPDK is an instance of ''decompositional'' kernels \cite{convolution-kernel} based on the idea of counting the number of common small subgraphs between two graphs.
+The subgraphs are pairs of neighborhoods whose roots are at a short distance.
 
@@
 
-Related to exact matching function, this function needs to solve the graph isomorphism problem.
+% Related to exact matching function, this function needs to solve the graph isomorphism problem.
 This problem is not known to be solvable in polynomial time nor to be NP-complete.
@@
 \subsection{Joint neighborhood subgraphs link prediction}
-Given a graph $G(V,E)$ and a set of links $L = \lbrace(u,v)\ |\ (u,v)\in\ O\ or\ (u,v)\in U \rbrace$, our method consists five steps:
+
+We propose to cast the link prediction problem
+
+In the link prediction problem we are given a graph $G(V,E)$ and a binary target vector $Y=\{y_{(0,0)},y_{(0,1)}, \cdots, y_{(|V|,|V|)}\}$ where $y_{(u,v)}=1$ if $(u,v) \in E$ and 0 otherwise.
+The training data is obtained considering a random subset of edges in $E^{tr} \in E$ and inducing a training graph $G^{tr}=(V,E^{tr})$.
+The remaining edges $E^{ts} = E \setminus E^{tr}$
+
 \begin{itemize}

### 2017-06-30 paper.tex
F

@@
 \subsection{Link encoding as subgraphs union}
+\label{sec:link}
 Most methods for link prediction compute pairwise nodes similarities treating  the nodes defining the candidate edge independently.
@@
 Finally we add an auxiliary node $w$ and the necessary edges to connect it to $u$ and $v$ (see Fig.\ref{key}).
+\figurename{fig:g}
 
@@
 
-We propose to cast the link prediction problem
-
 In the link prediction problem we are given a graph $G(V,E)$ and a binary target vector $Y=\{y_{(0,0)},y_{(0,1)}, \cdots, y_{(|V|,|V|)}\}$ where $y_{(u,v)}=1$ if $(u,v) \in E$ and 0 otherwise.
 The training data is obtained considering a random subset of edges in $E^{tr} \in E$ and inducing a training graph $G^{tr}=(V,E^{tr})$.
-The remaining edges $E^{ts} = E \setminus E^{tr}$
-
-\begin{itemize}
-	\item Node labeling: Nodes in $G$ are labeled using a defined node label function $\ell$.
-	\item Link representing: Link in $L$ are represented as joint neighborhood subgraphs. As a result, we have a set of graphs $SG = \lbrace G_{uv}\ |\ (u,v) \in L \rbrace$
-	\item Kernel computation: Obtained graph set $SG$ is used to compute a gram matrix, $K$, by using NSPDK. $K$ shows the similarities between graphs (links).
-	\item Model configuration: $K$ is then fed into a kernel machine to build a model which tries to learn a function to separate observed links from non-observed ones in the sense of properties.
-	\item Scoring and ranking: Now the model is used to return scores for coming links. These scores are used to rank links from the most to the least probable of being present in the graph.
-\end{itemize}
+The remaining edges $E^{ts} = E \setminus E^{tr}$ are used to partition the target vectors: $Y^{tr} = \{y_{(u,v)} | (u,v) \in E^{tr}\}$, $Y^{ts} = \{y_{(u,v)} | (u,v) \in E^{ts}\}$.
+We then build a train and test set as the corresponding joint neighborhood subgraphs as detailed in Section~\ref{sec:link}.
+We have now cast the problem in a standard classification problem in the domain of graphs.
 

### 2017-06-30 paper.tex
F

@@
 The remaining edges $E^{ts} = E \setminus E^{tr}$ are used to partition the target vectors: $Y^{tr} = \{y_{(u,v)} | (u,v) \in E^{tr}\}$, $Y^{ts} = \{y_{(u,v)} | (u,v) \in E^{ts}\}$.
-We then build a train and test set as the corresponding joint neighborhood subgraphs as detailed in Section~\ref{sec:link}.
-We have now cast the problem in a standard classification problem in the domain of graphs.
+We can now cast the problem as a standard classification problem in the domain of graphs.
+Given $G^{tr}$ we build a train and test set as the corresponding joint neighborhood subgraphs as detailed in Section~\ref{sec:link}.
+We can now compute a Gram matrix of the instances and solve the task using the LinearSVC library.
 

### 2017-06-30 paper.tex
F

@@
 Given $G^{tr}$ we build a train and test set as the corresponding joint neighborhood subgraphs as detailed in Section~\ref{sec:link}.
-We can now compute a Gram matrix of the instances and solve the task using the LinearSVC library.
+We can now compute a Gram matrix of the instances and solve the classification task using for example the efficient LinearSVC library.
 
 \section{Experiment}
-In this section, we intend to measure the performance of our proposed method and compare it with other link prediction methods.
-We follow the procedure used in \cite{matrix-factorization} which employs six datasets in different domains.
-In the following we shortly describe each dataset.
+To compare the performance of the JNSL method with other link prediction approaches we follow \cite{matrix-factorization} and use 6 datasets belonging to different domains.
 \begin{itemize}
-\item \textit{Protein }\cite{protein-protein}: the medium confidence network which encodes the interaction between proteins. It contains 2617 nodes and 11855 links. The average degree is 9.1.
+\item \textit{Protein }\cite{protein-protein}: nodes are proteins and edges encodes a thresholded interaction confidence between proteins.
+It has 2617 nodes and 11855 links with a median degree of 9.1.
 
-\item \textit{Metabolic} \cite{metabolic}: a biological network which relates enzyme proteins and chemical compounds and it includes 668 nodes and 2782 links. The average degree is 8.3.
+\item \textit{Metabolic} \cite{metabolic}: nodes are enzyme and metabolites, edges are present if the enzyme catalyzes for a reaction that include those chemical compounds.
+It has 668 nodes and 2782 links with a median degree of 8.3.
 

### 2017-06-30 paper.tex
F

@@
 
-\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference from the first to the $12^{th}$ edition.
-Nodes are authors and links encode co-author relation between authors.
-This network contains 2865 nodes and 4733 links.
-The average degree is 3.3.
+\item \textit{Nips} \cite{nips}: nodes are authors at the NIPS conference from the first to the $12^{th}$ edition.
+Links encode the co-authorhip relation, i.e.
+if two authors have published a paper together.
+This network contains 2865 nodes and 4733 links with a median degree of 3.3.
 
-\item \textit{Condmat} \cite{condmat}: a network of co-authors for condensed matter physists. This network has 14230 nodes and 1196 links. The average degree is 0.17.
+\item \textit{Condmat} \cite{condmat}: nodes are scientists working in condensed matter physics, edges encode co-authorship. This network has 14230 nodes and 1196 links with a median degree of 0.17.
 

### 2017-06-30 paper.tex
F

@@
 
-\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: a network describing the dispute between 130 countries.
-A link connecting two nodes (countries) if they dispute.
-We have 180 links in total in this network.
-The average degree is 2.5.
+\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: nodes are countries and edges encode a conflict or a dispute.
+We have 130 nodes and 180 links in total in this network with a median degree of 2.5.
 
@@
 
-We evaluate the performance of employed methods via a 10 splits.
-Each round, a given ratio of links will be used to train models, and the rest of links are used to test.
-For \textit{Protein}, \textit{Metabolic}, \textit{Nips} and \textit{Conflict} networks, we set the training ratio to 10$\%$ while the training ratio for \textit{Condmat} and \textit{Powergrid} to 90$\%$.
-The performance of each method is computed by taking an average of ROC-AUC over 10 rounds.
+We evaluate the performance of employed methods splitting 10 times the data in a train and a test part.
+For \textit{Protein}, \textit{Metabolic}, \textit{Nips} and \textit{Conflict} networks, we use 10$\%$ of the edges to induce the training set while for \textit{Condmat} and \textit{Powergrid} we use 90$\%$ of the links.
+The performance of each method is computed as the average of the AUC-ROC over the 10 rounds.
 

### 2017-06-30 paper.tex
F

@@
 \item \textit{Protein }\cite{protein-protein}: nodes are proteins and edges encodes a thresholded interaction confidence between proteins.
-It has 2617 nodes and 11855 links with a median degree of 9.1.
+It has 2617 nodes and 11855 links with an average degree of 9.1.
 
 \item \textit{Metabolic} \cite{metabolic}: nodes are enzyme and metabolites, edges are present if the enzyme catalyzes for a reaction that include those chemical compounds.
-It has 668 nodes and 2782 links with a median degree of 8.3.
+It has 668 nodes and 2782 links with an average degree of 8.3.
 
@@
 if two authors have published a paper together.
-This network contains 2865 nodes and 4733 links with a median degree of 3.3.
+This network contains 2865 nodes and 4733 links with an average degree of 3.3.
 
-\item \textit{Condmat} \cite{condmat}: nodes are scientists working in condensed matter physics, edges encode co-authorship. This network has 14230 nodes and 1196 links with a median degree of 0.17.
+\item \textit{Condmat} \cite{condmat}: nodes are scientists working in condensed matter physics, edges encode co-authorship. This network has 14230 nodes and 1196 links with an average degree of 0.17.
 
 \item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: nodes are countries and edges encode a conflict or a dispute.
-We have 130 nodes and 180 links in total in this network with a median degree of 2.5.
+We have 130 nodes and 180 links in total in this network with an average degree of 2.5.
 

### 2017-06-30 paper.tex
Image add

@@
 We then consider the graph $\mathcal{J}$ induced by the set union $N_R(u) \cup N_R(u)$.
-Finally we add an auxiliary node $w$ and the necessary edges to connect it to $u$ and $v$ (see Fig.\ref{key}).
-\figurename{fig:g}
+Finally we add an auxiliary node $w$ and the necessary edges to connect it to $u$ and $v$ (see Fig.\ref{fig:example}).
+\begin{figure}
+\centering
+\includegraphics[height=2.2cm]{subgraphs}
+\caption{Example of joint neighborhood subgraphs.}
+\label{fig:example}
+\end{figure}
 
@@
 Given $G^{tr}$ we build a train and test set as the corresponding joint neighborhood subgraphs as detailed in Section~\ref{sec:link}.
-We can now compute a Gram matrix of the instances and solve the classification task using for example the efficient LinearSVC library.
+We can now compute a Gram matrix of the instances and solve the classification task using for example the efficient LinearSVC library \cite{svm}.
 
@@
 
+\bibitem{svm} http://www.scikit-learn.org/
+
 %\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular

### 2017-06-30 paper.tex
F

@@
 \centering
-\includegraphics[height=2.2cm]{subgraphs}
-\caption{Example of joint neighborhood subgraphs.}
+\includegraphics[width=.9\textwidth]{subgraphs}
+\caption{Left) a given network. Right) joint neighborhood subgraphs for an existing (top) and a non existing link (bottom).}
 \label{fig:example}
@@
 \end{table}
+
 \section{Conclusion and Future Work}
-In this paper, we have proposed an effective method for link prediction.
-Our method takes advantages from the way to represent links as joint neighborhood subgraphs and the employment of an convolution kernel that is able to efficiently exploit the graph structure.
-The results from the experiment show that our method is the state of the art for graph structured link prediction, especially when the side information are not available.
-
-For the future work, we plan to investigate to propose a method for link prediction which can make use of the variety of information sources associated with graphs.
+We have presented a novel approach to link prediction in absence of side information that can effectively exploit the topological contextual information available in a neighborhood of each edge.
+We have empirically shown that this approach achieves very competitive results compared to other state-of-the-art methods.
+In the future, we will investigate how to make use of multiple and heterogeneous information sources when these are available for nodes and edges.
 

### 2017-06-30 paper.tex
F

@@
 \section{Results and Discussion}
-Table \ref{result_table} shows the performance of link prediction methods in ROC-AUC on six datasets in which we mark as bold for the best ROC-AUC on each dataset.
+In table \ref{result_table} we report the performance of link prediction methods measured as the AUC-ROC value on 6 datasets.
 From the results on the table, we can group methods into two groups based on their performances: supervised methods and unsupervised methods.
@@
 \begin{table}
-\caption{The ROC-AUC performance on six datasets of different link prediction methods in which AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top: Liear regression running on unsupervised scores \cite{matrix-factorization}:, SVD \cite{matrix-factorization}:: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores.
-}
+\caption{AUC-ROC performance on 6 datasets.
+Legend: AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top: Liear regression running on unsupervised scores \cite{matrix-factorization}:, SVD \cite{matrix-factorization}:: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores, JNSL: joint neighborhood subgraph link (our method).
+In bold the highest score.}
 \centering

### 2017-06-30 paper.tex
F

@@
 \begin{abstract}
-Graphs are common data structure used to represent data in which the relation between entities are encoded.
+The amount of relational data is increasing rapidly.
+These datasets are best represented as networks or graphs.
+A key characteristic of this type of data collections is the sparseness and dynamic nature.
+A crucial computational task is then the ''link prediction problem'' which allows to suggest possible collaborators for scientists in social networks, or to discover unknown interactions between proteins to explain the mechanism of a disease in biological networks, or to suggest novel products to be bought to a customer in a e-commerce recommendation system.
+Most approaches however do not effectively exploit the topological contextual information available in a neighborhood of each edge.
+Here we propose to cast the problem as a binary classification task over specific subgraphs and employ efficient graph kernels to solve it.
+
+% Graphs are common data structure used to represent data in which the relation between entities are encoded.
 A number of graph-based methods and systems have been proposed, varying from biology to recommendation to social network.
@@
 In general supervised methods exhibit better accuracies compared to unsupervised methods although incurring in much higher computational and memory complexity costs.
-Moreover, most approaches implicitly represent the link prediction problem and the inference used to tackle it as a disjunction over the edges, that is, information on edges is propagated in an additive fashion so that for a node to have $k$ neighbors or $k+1$ does not make a drastic difference.
+Moreover, most approaches implicitly represent the link prediction problem and the inference used to tackle it as a disjunction over the edges, that is, information on edges is propagated in such a fashion so that for a node to have $k$ neighbors or $k+1$ does not make a drastic difference.
 We claim that this hypothesis is likely putting a cap on the discriminative power of classifiers and therefore we propose a novel supervised method that employs a conjunctive representation.

### 2017-06-30 paper.tex
F

@@
 A crucial computational task is then the ''link prediction problem'' which allows to suggest possible collaborators for scientists in social networks, or to discover unknown interactions between proteins to explain the mechanism of a disease in biological networks, or to suggest novel products to be bought to a customer in a e-commerce recommendation system.
-Most approaches however do not effectively exploit the topological contextual information available in a neighborhood of each edge.
-Here we propose to cast the problem as a binary classification task over specific subgraphs and employ efficient graph kernels to solve it.
+Most approaches however do not effectively exploit the topological contextual information available in the neighborhood of each edge.
+Here we cast the problem as a binary classification task over specific subgraphs and employ efficient graph kernels to solve it and show empirically state-of-the-art results on several benchmark datasets.
 
@@
 An empirical experiment on different datasets proves that our proposed method shows the state of the art for link prediction.
-\keywords{Link prediction, joint neighborhood subgraphs}
+\keywords{Link prediction, graph kernels}
 \end{abstract}

### 2017-06-30 paper.tex
F

@@
 Most approaches however do not effectively exploit the topological contextual information available in the neighborhood of each edge.
-Here we cast the problem as a binary classification task over specific subgraphs and employ efficient graph kernels to solve it and show empirically state-of-the-art results on several benchmark datasets.
+Here we cast the problem as a binary classification task over specific subgraphs and employ efficient graph kernels to solve it.
+We show empirically state-of-the-art results on several benchmark datasets.
 
@@
 Finally we add an auxiliary node $w$ and the necessary edges to connect it to $u$ and $v$ (see Fig.\ref{fig:example}).
+
 \begin{figure}
@@
 \includegraphics[width=.9\textwidth]{subgraphs}
-\caption{Left) a given network. Right) joint neighborhood subgraphs for an existing (top) and a non existing link (bottom).}
+\caption{Left) We represent with solid lines edges belonging to the training material and with a dotted line edges belonging to the test material.
+Right) joint neighborhood subgraphs for an existing (green endpoints) (top) and a non existing (red endpoints) link (bottom).
+These graphs will receive respectively a positive and a negative target.}
 \label{fig:example}

### 2017-08-01 paper.tex
abstract and corrections

@@
 \begin{abstract}
-The amount of relational data is increasing rapidly.
-These datasets are best represented as networks or graphs.
-A key characteristic of this type of data collections is the sparseness and dynamic nature.
-A crucial computational task is then the ''link prediction problem'' which allows to suggest possible collaborators for scientists in social networks, or to discover unknown interactions between proteins to explain the mechanism of a disease in biological networks, or to suggest novel products to be bought to a customer in a e-commerce recommendation system.
-Most approaches however do not effectively exploit the topological contextual information available in the neighborhood of each edge.
-Here we cast the problem as a binary classification task over specific subgraphs and employ efficient graph kernels to solve it.
-We show empirically state-of-the-art results on several benchmark datasets.
+A crucial computational task for relational and network data is the ''link prediction problem'' which allows for example to discover unknown interactions between proteins to explain the mechanism of a disease in biological networks, or to suggest novel products for a customer in a e-commerce recommendation system.
+Most approaches however do not effectively exploit the contextual information available in the neighborhood of each edge.
+Here we propose to cast the problem as a binary classification task over the union of the pair of subgraphs located at the endpoints of each edge.
+We model the classification task using a support vector machine endowed with an efficient graph kernel and achieve state-of-the-art results on several benchmark datasets.
 
@@
 
-Unsupervised learning methods are non-adaptive, and hence computationally efficient, and define a score for any node pair that is proportional to the existence likelihood of an edge between the two nodes.
+Unsupervised methods are non-adaptive (i.e.
+they do not have parameters that are tuned on the specific problem instance), and can therefore be computationally efficient.
+In general they define a score for any node pair that is proportional to the existence likelihood of an edge between the two nodes.
 \textit{Adamic-Adar} \cite{adamic} computes the weighted sum over the common neighbors where the weight is inversely proportional to the (log of) each neighbor node degree.
@@
 The training data is obtained considering a random subset of edges in $E^{tr} \in E$ and inducing a training graph $G^{tr}=(V,E^{tr})$.
+Note that the graph used for training does not contain any of the edges that will be queried in the test phase.
 The remaining edges $E^{ts} = E \setminus E^{tr}$ are used to partition the target vectors: $Y^{tr} = \{y_{(u,v)} | (u,v) \in E^{tr}\}$, $Y^{ts} = \{y_{(u,v)} | (u,v) \in E^{ts}\}$.
@@
 
-\section{Experiment}
+\section{Empirical evaluation}
 To compare the performance of the JNSL method with other link prediction approaches we follow \cite{matrix-factorization} and use 6 datasets belonging to different domains.
@@
 
-\textbf{Model Selection}: The values of different hyper-parameters are set by using a 3-fold on training set in which we use one fold for training and the rest two folds for validation.
+\textbf{Model Selection}: The values of different hyper-parameters are set by using a 3-fold on the training set, that is, always considering only the training network, we use one fold for fitting the parameters and the rest two folds for validating the effect of the hyper parameter choice.
 We tune the values of radius for extracting subgraphs $R$ in $\lbrace 1, 2 \rbrace$, $\lambda$ in node label function in $\lbrace 10, 15 \rbrace$, for $r$ and $d$ parameters of NSPDK in $\lbrace  1, 2 \rbrace$ and $\lbrace  1, 2, 3 \rbrace$, respectively.
@@
 \section{Conclusion and Future Work}
-We have presented a novel approach to link prediction in absence of side information that can effectively exploit the topological contextual information available in a neighborhood of each edge.
+We have presented a novel approach to link prediction in absence of side information that can effectively exploit the topological contextual information available in the neighborhood of each edge.
 We have empirically shown that this approach achieves very competitive results compared to other state-of-the-art methods.
-In the future, we will investigate how to make use of multiple and heterogeneous information sources when these are available for nodes and edges.
+In future work, we will investigate how to make use of multiple and heterogeneous information sources when these are available for nodes and edges.
 

### 2017-08-03 paper.tex
Add files via upload

@@
 %
-\authorrunning{Dinh Tran Van, Alessandro Sperduti, and Fabrizio Costa$^2$}
+\authorrunning{Dinh Tran-Van, Alessandro Sperduti, and Fabrizio Costa$^2$}
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 \begin{abstract}
-A crucial computational task for relational and network data is the ''link prediction problem'' which allows for example to discover unknown interactions between proteins to explain the mechanism of a disease in biological networks, or to suggest novel products for a customer in a e-commerce recommendation system.
-Most approaches however do not effectively exploit the contextual information available in the neighborhood of each edge.
+A crucial computational task for relational and network data is the ``link prediction problem'' which allows for example to discover unknown interactions between proteins to explain the mechanism of a disease in biological networks, or to suggest novel products for a customer in a e-commerce recommendation system.
+Most link prediction approaches however do not effectively exploit the contextual information available in the neighborhood of each edge.
 Here we propose to cast the problem as a binary classification task over the union of the pair of subgraphs located at the endpoints of each edge.
@@
 
-% Graphs are common data structure used to represent data in which the relation between entities are encoded.
-A number of graph-based methods and systems have been proposed, varying from biology to recommendation to social network.
-Most methods have to take partially observed graphs as the input to proceed due to the lack of information.
-This prevents them from showing promising results.
-Link prediction becomes an effective paradigm to solve this problem.
-However, most existing link prediction methods are based on the transitive manner which cannot effectively exploit graph structures.
-Here we propose a method that first represents each link between two nodes by a graph composed of their neighborhood subgraphs.
-We then employ a decompositional graph kernel to measure the similarity between links.
-An empirical experiment on different datasets proves that our proposed method shows the state of the art for link prediction.
 \keywords{Link prediction, graph kernels}
@@
 This yields collections that are best represented as graphs or relational data bases and requires a more complex form of analysis.
-As cursory examples of application domains that are particularly  it is sufficient to mention social networks, where nodes are people and edges encode a type of association such as friendship or co-authorship, bioinformatics, where nodes are proteins and metabolites and edges represent a type of chemical interaction such as catalysis or signaling, and e-commerce, where nodes are people and goods and edges encode a ''buy'' or ''like'' relationship.
+As cursory examples of application domains that are social networks, where nodes are people and edges encode a type of association such as friendship or co-authorship, bioinformatics, where nodes are proteins and metabolites and edges represent a type of chemical interaction such as catalysis or signaling, and e-commerce, where nodes are people and goods and edges encode a ``buy'' or ``like'' relationship.
 A key characteristic of this type of data collections is the sparseness and dynamic nature, i.e.
 the fact that the number of recorded relations is significantly smaller than the number of all possible pairwise relations, and the fact that these relations evolve in time.
-A crucial computational task is then the ''link prediction problem'' which allows to suggest friends, or possible collaborators for scientists in social networks, or to discover unknown interactions between proteins to explain the mechanism of a disease in biological networks, or to suggest novel products to be bought to a customer in a e-commerce recommendation system.
-The many approaches to link prediction that exist in literature can be partitioned according to 1) whether additional or ''side'' information is available for nodes and edges or rather only the network topology is considered and 2) whether the approach is unsupervised or supervised.
+A crucial computational task is then the ``link prediction problem'' which allows to suggest friends, or possible collaborators for scientists in social networks, or to discover unknown interactions between proteins to explain the mechanism of a disease in biological networks, or to suggest novel products to be bought to a customer in a e-commerce recommendation system.
+Many approaches to link prediction that exist in literature can be partitioned according to \textit{i}) whether additional or ``side'' information is available for nodes and edges or rather only the network topology is considered and \textit{ii}) whether the approach is unsupervised or supervised.
 
@@
 \textit{Adamic-Adar} \cite{adamic} computes the weighted sum over the common neighbors where the weight is inversely proportional to the (log of) each neighbor node degree.
-The \textit{preferential attachment} method computes a score simply as the product of the node degrees in an attempt to exploit the 'rich get richer' property of certain network dynamics.
+The \textit{preferential attachment} method computes a score simply as the product of the node degrees in an attempt to exploit the ``rich get richer'' property of certain network dynamics.
 \textit{Katz} \cite{katz} takes into account the number of common paths with different lengths between two nodes, assigning more weight to shorter paths.
@@
 We claim that this hypothesis is likely putting a cap on the discriminative power of classifiers and therefore we propose a novel supervised method that employs a conjunctive representation.
-We call the method ''joint neighborhood subgraphs link prediction'' (JNSL).
+We call the method ``joint neighborhood subgraphs link prediction'' (JNSL).
 The key idea here is to transform the link prediction task into a binary classification on suitable small subgraphs which we then solve using an efficient graph kernel method.
@@
 The set $E$ is partitioned into the subset of observed links ($O$) and the subset of unobserved links ($U$).
-Like other approaches we assume that all unobserved links are indeed ''non-links'' and we therefore define the link prediction problem as the task of ranking candidate links from the most to the least probable to recover links in $O$ but not in $U$ exploiting only the network topology.
+Like other approaches we assume that all un-observed links are indeed ``non-links'' and we therefore define the link prediction problem as the task of ranking candidate links from the most to the least probable to recover links in $O$ but not in $U$ exploiting only the network topology.
 
 We define the \textit{distance} $\mathcal{D}(u,v)$ between two nodes $u$ and $v$, as the number of edges on the shortest path between them.
-The \textit{neighborhood} of a node $u$ with radius $r$, $N_r(u) = \lbrace v\ |\ d(u,v) \leq r \rbrace$, is the set of nodes at distance no greater than $r$ from $u$.
+The \textit{neighborhood} of a node $u$ with radius $r$, $N_r(u) = \lbrace v\ |\ \mathcal{D}(u,v) \leq r \rbrace$, is the set of nodes at distance no greater than $r$ from $u$.
 The corresponding \textit{neighborhood subgraph} $\mathcal{N}_{r}^{u}$ is the  subgraph induced by the neighborhood (i.e.
@@
 Most methods for link prediction compute pairwise nodes similarities treating  the nodes defining the candidate edge independently.
-Instead we propose to jointly consider both candidate endpoint nodes together with their extended ''context''.
+Instead we propose to jointly consider both candidate endpoint nodes together with their extended ``context''.
 To do so we build a graph starting from the two nodes and the underlying network.
@@
 We propose to use a graph kernel approach to classify the subgraphs encoding each link.
-In our setup nodes are not endowed with any ''side'' information.
+In our setup nodes are not endowed with any ``side'' information.
 However to increase the discriminative power of the similarity notion induced by the graph kernel, instead of assuming a dummy, non-informative label on each node, we propose to use a node labeling function $\ell$ which assigns as the discrete label the node degree.
@@
 where $i = \lceil \frac{d(u)-T}{bin}\rceil$, $bin = \frac{d(G)-T}{\lambda - T}$ and $\lambda$ ($\lambda > T$) is the maximum number of symbols used.
-The value of $\lambda$ depend on the degree distribution and can be tuned as a hyperparameter of the approach.
+The value of $\lambda$ depends on the degree distribution and can be tuned as a hyperparameter of the approach.
 
@@
 Here we briefly describe an efficient graph kernel called the Neighborhood Subgraph Pairs Distance kernel (NSPDK) introduced in \cite{nspdk}.
-NSPDK is an instance of ''decompositional'' kernels \cite{convolution-kernel} based on the idea of counting the number of common small subgraphs between two graphs.
+NSPDK is an instance of ``decompositional'' kernels \cite{convolution-kernel} based on the idea of counting the number of common small subgraphs between two graphs.
 The subgraphs are pairs of neighborhoods whose roots are at a short distance.
@@
 
-We evaluate the performance of employed methods splitting 10 times the data in a train and a test part.
+We evaluate the performance of employed methods by splitting 10 times the data in a train and a test part.
 For \textit{Protein}, \textit{Metabolic}, \textit{Nips} and \textit{Conflict} networks, we use 10$\%$ of the edges to induce the training set while for \textit{Condmat} and \textit{Powergrid} we use 90$\%$ of the links.
@@
 
-\section{Results and Discussion}
-In table \ref{result_table} we report the performance of link prediction methods measured as the AUC-ROC value on 6 datasets.
+\section{Results and discussion}
+In Table \ref{result_table}, we report the performance of link prediction methods measured as the AUC-ROC value on 6 datasets.
 From the results on the table, we can group methods into two groups based on their performances: supervised methods and unsupervised methods.
@@
 \caption{AUC-ROC performance on 6 datasets.
-Legend: AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top: Liear regression running on unsupervised scores \cite{matrix-factorization}:, SVD \cite{matrix-factorization}:: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores, JNSL: joint neighborhood subgraph link (our method).
+Legend: AA: Adamic-Adar, PA \cite{pa} preferential Attachment, SHP: Shortest Path, Sup-Top \cite{matrix-factorization}: Liear regression running on unsupervised scores, SVD \cite{matrix-factorization}: Singular value decomposition, Fact+Scores \cite{matrix-factorization}: Factorization with unsupervised scores, JNSL: joint neighborhood subgraph link (our method).
 In bold the highest score.}
@@
 
-\section{Conclusion and Future Work}
+\section{Conclusion and future work}
 We have presented a novel approach to link prediction in absence of side information that can effectively exploit the topological contextual information available in the neighborhood of each edge.
